Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-07-18 doc/ms.tex
Update text regarding velocity fits to better reflect more recent numerical work.

\subsection{Light Curve Fit}
\label{sec:lc_fit}

@@

\subsection{Expansion Velocity Fit}
\label{sec:early_vel}

As previously noted, $t_0$ does not correspond to the time of 
explosion, $t_\mathrm{exp}$, for type Ia SNe as the SN may 
experience a dark phase following shock breakout before radioactive 
energy can diffuse to the photosphere. \citet{2014ApJ...784...85P} 
instead suggest that measurements of the photospheric velocity be 
used to determine $t_\mathrm{exp}$ given that the ejecta begin 
expanding from the moment of explosion.  Assuming a
constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} 
find that the photospheric velocity evolves as
$v_{ph}\propto(t-t_{exp})^{-0.22}$. While the photospheric velocity
is not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
can be used as a proxy
\citep{2014ApJ...784...85P,2016ApJ...826..144S}.

In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
likely due to high temperatures in the ejecta. Thus, we
determine the photospheric velocity from the 
\ion{Si}{2}\,$\lambda$6355 line. Visual inspection shows no 
sign of multi-velocity components of \ion{Si}{2}, and that 
\ion{C}{2}\,$\lambda$6580 line overlaps the red
wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model the observed 
spectra between 5,900 and 6,500\,\AA (rest-frame) as the combination 
of two gaussian kernels plus a linear baseline, which
accounts for \ion{Si}{2}, \ion{C}{2} and the
continuum, respectively. The expansion
velocity of \ion{Si}{2} is measured by the central wavelength
of the \ion{Si}{2} Gaussian kernel.

@@

We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\;\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}). Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitively of the result on the assumed power-law index. We find that this variation in the power-law index result in inferred explosion times that vary by $\approx$1 d (Figure \ref{fig:velocity_t_exp}). Given the theorhetical expectation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.45 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).

Comparing our estimates for $t_{exp}$ and $t_0$ (left panel of 
Figure \ref{fig:velocity_t_exp}), we find that 
$t_0\lessapprox t_{exp}$.
Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
conclusion that $t_0\simeq t_{exp}$, which is consistent to within the uncertainties.

>>>>

\subsection{Time of First Light from the Early Light Curve}
\label{sec:lc_fit}

@@

\subsection{Time of Explosion from the Photospheric Velocity}
\label{sec:early_vel}

As previously noted, $t_0$ does not correspond to the time of 
explosion, $t_\mathrm{exp}$, for type Ia SNe as the SN may 
experience a dark phase following shock breakout before radioactive 
energy can diffuse to the photosphere. \citet{2014ApJ...784...85P} 
instead suggest that measurements of the photospheric velocity be 
used to determine $t_\mathrm{exp}$ given that the ejecta begin 
expanding from the moment of explosion.  Assuming a
constant opacity in the ejecta, \citeauthor{2014ApJ...784...85P} 
find that the photospheric velocity evolves as
$v_{ph}\propto(t-t_\mathrm{exp})^{-0.22}$. Numerical experiments by \citet{2016ApJ...826...96P} find that the consatnt-opacity assumption strongly depends on the amount of $^{56}$Ni mixing in the SN ejecta (for a more detailed discussion of $^{56}$Ni mixing see \S\ref{sec:Ni_mixing}). As a result, the adoption of a $t^{-0.22}$ power-law model may not be valid for all SNe Ia. Nevertheless, we proceed on the assumption that \abc\ experienced strong $^{56}$Ni mixing, corresponding to the models that are best approximated as a $t^{-0.22}$ power law. We do this in part to compare with previous studies, though we caution that our derived value for $t_{exp}$ is subject to uncertainties related to ejecta mixing.

While the photospheric velocity
is not easy to measure, line velocities of \ion{Si}{2} or \ion{Ca}{2}
can be used as a proxy
\citep{2014ApJ...784...85P,2016ApJ...826..144S}. In the case of \abc, the \ion{Ca}{2} IR triplet is very weak, 
likely due to high temperatures in the ejecta. Thus, we
determine the photospheric velocity from the 
\ion{Si}{2}\,$\lambda$6355 line. Visual inspection shows no 
sign of multi-velocity components of \ion{Si}{2}, and that 
the \ion{C}{2}\,$\lambda$6580 line overlaps the red
wing of the \ion{Si}{2} line (see Figures~\ref{fig:spec_seq} and \ref{fig:carbon}). Consequently, we model the observed 
spectra between 5,900 and 6,500\,\AA\ (rest-frame) as the combination 
of two gaussian kernels plus a linear baseline, which
accounts for \ion{Si}{2}, \ion{C}{2} and the
continuum, respectively. The expansion
velocity of \ion{Si}{2} is measured by the central wavelength
of the \ion{Si}{2} Gaussian kernel.

@@

We fit the measured velocities of \ion{Si}{2}\,$\lambda$6355 to the
$v\propto(t-t_{exp})^{-0.22}$ model by minimizing the $\chi^2$ value and find the best-fit explosion time relative to $T_{B,\mathrm{max}}$ in the SN rest frame to be $t_{exp} = -17.45 \pm ^{0.14}_{0.16}\;\textrm{d}$, where the uncertainties represent the 95\% confidence interval (Figure \ref{fig:velocity_t_exp}). Following the analysis in \citet{2014ApJ...784...85P}, we additionally alter the power-law index to $-0.20$ and $-0.24$ to examine the sensitivety of the result on the assumed power-law index. We find that this variation in the power-law index results in inferred explosion times that vary by $\approx$1 d (Figure \ref{fig:velocity_t_exp}). Given the analytical approximation that $v \propto t^{-0.22}$, we adopt $t_{exp} = -17.5 \pm 0.5 \; \mathrm{d}$, where the uncertainty reflects possible variations in the power-lax index (see \citealt{2014ApJ...784...85P}).

Comparing our estimates for $t_{exp}$ and $t_0$ (left panel of 
Figure \ref{fig:velocity_t_exp}), we find that 
$t_0\lessapprox t_{exp}$.
Since physical causality requires $t_{exp}<t_0$, we draw the qualitative
conclusion that $t_0\simeq t_{exp}$, which is consistent to within the uncertainties. Again, we caution that this derivation of $t_\mathrm{exp}$ relies on the assumption $v \propto t^{-0.22}$, which may not be valid for all SNe Ia.
